Extracting Function Signature from R Program Traces

### 2020-05-14 paper/main.tex
some data in evaluation

We found that \AT{in many cases}. the reverse dependencies increased the code coverage (this aligns with findings in \AT{cite genthat}), and this was especially true for the functions for which contract assertions failed.

>>>>

To try to detect this pattern, we cross-referenced functions with failing contract checks against the code coverage for that function from the package's tests.
For a given function, a coverage of X\% indicates that X\% of the code in the function body was executing by running package test, example, and vignette code.
Of the remaining failed contracts, we found that \~28\% of them were from functions which had less than 100\% coverage, meaning that it is possible that \typetracer failed to synthesize the correct type for the function as not all possible executions were recorded.
